\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-26 document/ms.tex
a few words about assumptions in summary

For each transit candidate, we constrain the physical parameters of the system
by fitting a section of light curve around each transit using an exposure-time
integrated  Keplerian orbit with a quadratic limb darkening law for the
central body\footnote{Implemented at \url{https://github.com/dfm/transit};
this \paper\ uses git commit \textsf{482d99b} of that repository.}.
It has previously been established that the orbital period of a transiting
planet with only one transit can still be constrained given a measurement of
the stellar density and an assumption about the orbital eccentricity \cite[for
example][]{Wang:2015, Osborn:2016}.
Qualitatively this works because the transit of a bound body cannot have an
arbitrary period for a given duration.
This is the same argument used to justify the ``photoeccentric effect''
\citep{Dawson:2012} and the method of ``asterodensity profiling''
\citep{Kipping:2014b}.
In particular, this suggests that the periods of single transits in systems
with multiple inner planets will be especially well constrained
\citep{Kipping:2012}.
In this \paper, we do not take advantage of the extra constraints provided by
the inner planets, instead treating each long-period transiting system in
isolation, but this would be a good follow-up project.

@@

\begin{figure*}~\\
\begin{center}
\includegraphics{figures/full_sample_plus_cands.pdf}
\end{center}
\caption{%
The catalog of long-period transiting exoplanet candidates (green points with
error bars) compared to the \kepler\ candidates (blue points) and confirmed
planets \citep[black points;][]{Morton:2016} found in our target sample, and
the Solar System (orange squares).
The vertical dashed line indicates the full lifetime of the \kepler\ Mission;
planets with orbital periods longer than this will show at most one transit.
The vertical solid line shows the absolute maximum period accessible to
transit searches that require at least three transits.
\dfmfiglabel{full-sample}}~\\
\end{figure*}

@@

To determine to what extent the catalog of detections presented in this work
may contain such false positives, we simulate populations of detected signals
to predict how many we should expect.  To accomplish this, we use the Python
package
\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
work we use commit \textsf{e4f54288}}, which
we developed for this purpose and utilizes the \project{isochrones}
package \citep{Morton:2015} for simulations of stellar populations.

@@

We have developed a fully automated method to search for the transits of
long-period exoplanets with only one or two observable transits in the
\kepler\ archival light curves.
This method uses probabilistic model comparison to veto non-transit signals.
Applying this method to the brightest \numtargets\ G/K dwarfs in the \kepler\
target list, we discover \numcands\ systems with likely astrophysical
transits and eclipses.
We fit the light curve for each candidate with a physical generative model and
informative priors on eccentricity and stellar density to estimate the
planet's orbital period.
Simulations of the false positive population~--~lone primary or secondary eclipses of
binary systems or background eclipsing binaries~--~suggest that 13 of these
candidates have high probability of being planetary in nature.

@@

% \dfmtodo{More words here about comparison and interpretation.}

These long-period exoplanet candidates are potentially interesting candidates
for follow-up observations.
Using a probabilistic mass--radius relationship, we predict the masses of our
candidates and report predictions for the radial velocity amplitudes.
Unfortunately, since the target stars are faint and the amplitudes are small,
these targets are unlikely to be accessible with even the current
state-of-the-art high-precision instruments.
We also discuss the potential for astrometric follow-up using the forthcoming
data from the \gaia\ Mission with similarly discouraging results.

@@

Follow-up observations would be fruitful in confirming the false-alarm
rates that we have estimated by further demonstrating that these planet
candidates are non-stellar.  Better characterization of the host stars with,
say, parallax measurements using \gaia would help further refine the
properties of their transiting planets.

@@

\acknowledgments
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful contributions to the ideas and code presented here.

@@

\appendix

>>>>

For each transit candidate, we constrain the physical parameters of the system
by fitting a section of light curve around each transit using an exposure-time
integrated  Keplerian orbit with a quadratic limb darkening law for the
central body\footnote{\url{https://github.com/dfm/transit}; in this work, we
use git commit \textsf{482d99b}.}.
It has previously been established that the orbital period of a transiting
planet with only one transit can still be constrained given a measurement of
the stellar density and an assumption about the orbital eccentricity \cite[for
example][]{Wang:2015, Osborn:2016}.
Qualitatively this works because the transit of a bound body cannot have an
arbitrary period for a given duration.
This is the same argument used to justify the ``photoeccentric effect''
\citep{Dawson:2012} and the method of ``asterodensity profiling''
\citep{Kipping:2014b}.
In particular, this suggests that the periods of single transits in systems
with multiple inner planets will be especially well constrained
\citep{Kipping:2012}.
In this \paper, we do not take advantage of the extra constraints provided by
the inner planets, instead treating each long-period transiting system in
isolation, but this would be a good follow-up project.

@@

\begin{figure*}~\\
\begin{center}
\includegraphics{figures/full_sample_plus_cands.pdf}
\end{center}
\caption{%
The catalog of long-period transiting exoplanet candidates (green points with
error bars) compared to the \kepler\ candidates (blue points) and confirmed
planets \citep[black points;][]{Morton:2016} found in our target sample, and
the Solar System (orange squares).
The thin black error bars to the left of each candidate indicate the minimum
period allowed for each candidate by the prior assumption that no other
transit occurred during the baseline of \kepler\ observations of the target.
The vertical solid line shows the absolute maximum period accessible to
transit searches that require at least three transits in the \kepler\ data.
\dfmfiglabel{full-sample}}~\\
\end{figure*}

@@

To determine to what extent the catalog of detections presented in this work
may contain such false positives, we simulate populations of detected signals
to predict how many we should expect.  To accomplish this, we use the Python
package
\exosyspop\footnote{\url{https://github.com/timothydmorton/exosyspop}; in this
work, we use git commit \textsf{e4f54288}.}, which
we developed for this purpose and utilizes the \project{isochrones}
package \citep{Morton:2015} for simulations of stellar populations.

@@

We have developed a fully automated method to search for the transits of
long-period exoplanets with only one or two observable transits in the
\kepler\ archival light curves.
This method uses probabilistic model comparison to veto non-transit signals.
Applying this method to the brightest \numtargets\ G/K dwarfs in the \kepler\
target list, we discover \numcands\ systems with likely astrophysical
transits and eclipses.
We fit the light curve for each candidate with a physical generative model and
informative priors on eccentricity and stellar density to estimate the
planet's orbital period.
The constraint on the period is also informed by the simplifying assumption
that no other transit could occur during the baseline of \kepler\ observations
of the target.
Simulations of the false positive population~--~lone primary or secondary
eclipses of binary systems or background eclipsing binaries~--~suggest that 13
of these candidates have high probability of being planetary in nature.

@@

Using a probabilistic mass--radius relationship, we predict the masses of our
candidates and report predictions for the radial velocity amplitudes.
Unfortunately, since the target stars are faint and the amplitudes are small,
these targets are unlikely to be accessible with even the current
state-of-the-art high-precision instruments.
We also discuss the potential for astrometric follow-up using the forthcoming
data from the \gaia\ Mission with similarly discouraging results.

Any detailed analysis of individual systems detected with only a single
transit requires follow-up observations to convincingly rule out false
positive scenarios and to better characterize the stellar host parameters
(with, for example, parallax measurements from \gaia).
The conclusions of this work~--~and all other occurrence rate results based on
\kepler\ data~--~are conditioned on the assumption that the stellar
characterization of the target sample is systematic and un-biased.
The main population-level results should be fairly insensitive systematic
issues with the sample but a rigorous analysis of these effects will be
required to come to more detailed conclusions about this population of
long-period transiting planets.

@@

@@

% \acknowledgments
\vspace{1.5em}
It is a pleasure to thank
Jeff Coughlin,
So Hattori,
Heather Knutson,
Hans-Walter Rix,
Dun Wang,
and
Angie Wolfgang
for helpful contributions to the ideas and code presented here.

@@

\newpage
\appendix
